### 2013-08-28 thesis/src/chapters/chapter-1.tex
Bibtex fix
Change footnote for a bib reference

\section{Motivation}
One of the keys factors that has driven transformation of computing industry in the last years is the perception of computing utilities as an ordinary property, which can be easily accessed and adjusted to a specific needs. That point of view resulted in profusion of different services, often collectively referred as a cloud computing. Similarly to services common to traditional markets, customers expect them to be accessible on demand and in easy manner, while paying only for the consumed goods. Furthermore, customers are interested in a given service provider only when it is eligible to guarantee appropriate quality of service.

@@

\subsection{Business}
The rapid growth of interest in cloud computing in recent years resulted in huge sums of money being invested in the field. Figure \ref{ch1:public-cloud-services-market-size} shows the size of the public cloud services market in 2012 and the forecast of its nearly two times growth in 2016. This data suggests that the subject is attractive for IT industry from the economic point of view. However, higher amounts of money spent on cloud services involve higher expectations of theirs quality from customers. Although the most significant players in cloud computing have been in the field for quite a long time, it is still possible to outline some deficiencies their products have. Additionally, lack of common standards hinder cooperation among different cloud providers. For example it is nearly impossible to create an autoscaling cloud federation with Amazon Web Services (current leader in providing cloud services\footnote{Gartner: Magic Quadrant for Cloud Infrastructure as a Service (Aug 2013)}) and another provider. What is more, Amazon AWS users cannot use more lightweight virtualization methods, such as linux containers. Nevertheless, when compared to other companies especially in terms of autoscaling capabilities, Amazon really shines. OpenShift, RedHat PaaS solution, ensures application scaling but with very limited possibilities of customisation of the process -- the user can only choose if their application should scale and the whole algorithm is solely based on the number of concurrent requests to the application. Users of Heroku, another PaaS solution, have no automation tool that would control the number of instances (\emph{dynos} in Heroku nomenclature) their application is running on -- they can change it manually.

>>>>

\section{Motivation}
One of the keys factors that has driven transformation of computing industry in the last years is the perception of computing utilities as an ordinary property, which can be easily accessed and adjusted to a specific needs. That point of view resulted in profusion of different services, often collectively referred as a cloud computing \cite{MeGr11}. Similarly to services common to traditional markets, customers expect them to be accessible on demand and in easy manner, while paying only for the consumed goods. Furthermore, customers are interested in a given service provider only when it is eligible to guarantee appropriate quality of service.

@@

\subsection{Business}
The rapid growth of interest in cloud computing in recent years resulted in huge sums of money being invested in the field. Figure \ref{ch1:public-cloud-services-market-size} shows the size of the public cloud services market in 2012 and the forecast of its nearly two times growth in 2016. This data suggests that the subject is attractive for IT industry from the economic point of view. However, higher amounts of money spent on cloud services involve higher expectations of theirs quality from customers. Although the most significant players in cloud computing have been in the field for quite a long time, it is still possible to outline some deficiencies their products have. Additionally, lack of common standards hinder cooperation among different cloud providers. For example it is nearly impossible to create an autoscaling cloud federation with Amazon Web Services (current leader in providing cloud services\cite{GartnerMagicQuadrantSep2013}) and another provider. What is more, Amazon AWS users cannot use more lightweight virtualization methods, such as linux containers. Nevertheless, when compared to other companies especially in terms of autoscaling capabilities, Amazon really shines. OpenShift, RedHat PaaS solution, ensures application scaling but with very limited possibilities of customisation of the process -- the user can only choose if their application should scale and the whole algorithm is solely based on the number of concurrent requests to the application. Users of Heroku, another PaaS solution, have no automation tool that would control the number of instances (\emph{dynos} in Heroku nomenclature) their application is running on -- they can change it manually.
